---
title: "Construal Level International Multilab Replication (CLIMR) Project: Pretest of Valence Differences in BIF Item Response Options"
author: "CLIMR Team"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: darkly
    toc: yes
    toc_float: yes
    keep_md: true
  pdf_document:
    toc: yes
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file, encoding = encoding, output_dir = "./reports/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("./R/validation/CLIMR-bif-valence-separate-pretest_import-analyze.R")
source("./R/validation/CLIMR-bif-valence-exploration.R")

```

# Overview

The documentation for this pretest is provided here: https://osf.io/g6d5v

# Separate Judgments of Item Response Options

When judged separately, the response options for each item are generally rated
such that the abstract option is more positively valenced than the concrete
option.

```{r}
bif_d %>% 
  knitr::kable()
```

Combining across the items, the valence difference in response options appears
to be non-trivial.

```{r}
bif_scale_smd
```

# Examination of the Effects of Valence Differences on Response Patterns

To assess the extent to which these valence differences might influence people's
responses to the BIF items, especially in an situation in which there is a
plausible motvation to provide more positive responses under some conditions, we
examined the data from Yan et al (2016, Experiment 3, 10.1093/jcr/ucw045). In
this experiment, participants were provided with a description of a socially
close or socially distant target and asked to complete the BIF. It is plausible
that people would want to provide more positive responses for a socially close
target, not for any reason related to construal level but for motivational
reasons.

The authors of this experiment graciously provided the original data, which we
used to fit models in which we predicted BIF responses using the social distance
manipulation and the BIF valence differences.

As a first look, we fit models predicting BIF responses from the distance
manipulation and tested whether adding random slopes for the items improved the
fit of the model. If there is substantial variance in the random slopes, that
would be an indication that there may extraneous influences (e.g., valence) on
the BIF responses. However, a likelihood ratio test indicates that there is no
significant improvement to the model offered by adding random slopes.

```{r}
lrt_rs
```

Next, we can examine the effect of adding the valence difference for each item
as a predictor in the model and also test if adding an interaction between
valence and the distance manipulation improves the model.

We see below that a series of LRTs indicates that adding valence does not offer
significant improvement to the model, nor does adding the interaction term.

```{r}
lrt_val
```

It can nevertheless be informative to examine the detailed model output.

As can be seen below, if the valence differences (as measured by the separate
judgments) had any influence on the responses to the BIF in this experiment,
those differences were minimal. Moreover, controlling for the valence 
differences did not meaningfully change the estimate of the effect of social
distance, suggesting that those effects were non-redundant.

```{r}
summary(model_soc)
```

```{r}
summary(model_val)
```

```{r}
summary(model_val_int)
```
